SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/encoding.tex
?? fixed
fixed-table0-intro-bio-exper

We have encoded the following variants of VTSs.
%
The variants are due to different combinations of constraints on the
activity on nodes and edges.
%
\begin{enumerate}[label=\Alph*]
\item Every present molecule is considered to be active.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
\item Activity of molecules on the edges is driven by pairing inhibition.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
\end{enumerate}
%
% For the version A, every present molecule is in active state.
%
In the table~\ref{table1}, we present the constraints involved in each version.
%
The column two of the table shows that the constraints V1-V8, R1-R2, and D1-D4 are present
for every variant.
%
The column three of the table lists the constraints that are different among the variants.
%
%
One of the restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
%
For example in version B, D, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
%
Similarly for the case of the edge in version C and D; Aeb.
%
In the case of versions F the activity of the molecules on the edges
is described by pairing matrix, if all the pairs of the present
molecule are present on the same edge than all of them inhibit each
other resulting in making all the molecules inactive, we term this
process ``pairing inhibition".
%
The constraints for the variants can be given to a SAT solver to find
VTSs that belong to the variants.

>>>>

We have encoded the following variants of VTSs.
%
The variants are due to different combinations of constraints on the
activity on nodes and edges.
%
\begin{enumerate}[label=\Alph*]
\item Every present molecule is considered to be active.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
\item Activity of molecules on the edges is driven by pairing inhibition.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
\end{enumerate}
%
% For the version A, every present molecule is in active state.
%
In the table~\ref{tab:grph}, we present the constraints involved in each version.
%
The column two of the table shows that the constraints V1-V8, R1-R2, and D1-D4 are present
for every variant.
%
The column three of the table lists the constraints that are different among the variants.
%
%
One of the restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
%
For example in version B, D, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
%
Similarly for the case of the edge in version C and D; Aeb.
%
In the case of versions F the activity of the molecules on the edges
is described by pairing matrix; Aep.

%if all the pairs of the present molecule are present on the same edge than all of them inhibit each other resulting in making all the molecules inactive, we term this process ``pairing inhibition".
%
The constraints for the variants can be given to a SAT solver to find
VTSs that belong to the variants.
